---
title: "mk3"
author: "jojoecp"
date: "5/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE,warning=FALSE}
library(tidyverse) #for data wrangling. very helpfull for preparing nodes and edges data
library(lubridate)
#library(network)
library(igraph)
library(tidygraph)
library(ggraph)
#library(visNetwork)
#library(networkD3)
# for twitter
library(rtweet)
```


```{r}
apikey <- "A5csjkdrS24vJ5ktiKYtgasFY"
apisecret <- "rNXrBbaRFVRmuHgEM5AMpdSoDp9gtfOr2KAosXz5xozhmKfPrF"
acctoken <- "1149867938477797376-xB3rmjq29qU8Alr9PBgGzkGumYU26j"
tokensecret <- "Dyf3VncHDtJZ8FhtnQ5GfSPWrOIFsxUGpCrNrj6Z7Q1xP"

token <- create_token(app = "Automated Twitter SNA",
                      consumer_key = apikey,
                      consumer_secret = apisecret,
                      access_token = acctoken,
                      access_secret = tokensecret)

get_token()
```

# CASE 1: @teamalgoritma ego network

- extract teamalgoritma follower
- filter only active follower, by:
  + last update (last 2 month)
  + follower and following (min 150 and 100)
- extract active follower's follower & following
  + from their follower - following subset, build:
    + friends network
    + influencer network
    + filter by high follower number as potential information spreading effectiveness


## Algoritma Detail Profile
```{r}
algo <- lookup_users("teamalgoritma")

folower <- get_followers("teamalgoritma",n = algo$followers_count,retryonratelimit = T)

detail_folower <- lookup_users(folower$user_id)
detail_folower <- data.frame(lapply(detail_folower,as.character),stringsAsFactors = F)

detail_folower %>% arrange(-as.numeric(followers_count)) %>% 
  select(screen_name,followers_count, friends_count, favourites_count)

detail_folower %>% filter(screen_name == "btekno")
table(as.factor(detail_folower$source))

active_fol <- detail_folower %>% 
  select(user_id,screen_name,created_at,followers_count,friends_count,favourites_count) %>%
  mutate(created_at = ymd_hms(created_at),
         followers_count = as.numeric(followers_count),
         friends_count = as.numeric(friends_count),
         favourites_count = as.numeric(favourites_count)) %>%
  filter((followers_count > 100 & followers_count < 6000), friends_count > 75, favourites_count > 10, 
         created_at > "2020-03-15" | is.na(created_at)) %>%
  arrange(-followers_count)


```

## Retrieve Algoritma Follower

```{r}
foler3 <- vector(mode = 'list', length = length(active_fol$screen_name))
names(foler3) <- active_fol$screen_name


flt_n <- function(x){
  if(x > 1500){
    x*0.5
  }else{x*0.75}
}

for (i in seq_along(active_fol$screen_name)) {
  message("Getting followers for user #", i+122, "/161")
  foler3[[i+122]] <- get_followers(active_fol$screen_name[i+122], 
                                  n = round(flt_n(active_fol$followers_count[i+122])), 
                                retryonratelimit = TRUE)
  
  if(i %% 5 == 0) Sys.sleep(5*60)
    message("sleep for 5 minutes") 
}

```

```{r}
fol3 <- bind_rows(foler3, .id = "screen_name")
all_folower <- rbind(fol1,fol2,fol3)
active_fol_x <- active_fol %>% select(user_id,screen_name)

all_folowerzz <- left_join(all_folower, active_fol_x, by="screen_name")

algo_follower <- all_folowerzz %>% select(user_id.x,user_id.y) %>%
  setNames(c("follower","active_user")) %>% 
  na.omit()

```


## Retrieve Algoritma Following

```{r}
friend_3 <- data.frame()

flt_n_2 <- function(x){
  if(x > 2000){
    x*0.4
  }else{x*0.65}
}

for (i in seq_along(active_fol$screen_name)) {
  message("Getting followers for user #", i+86, "/161")
  kk <- get_friends(active_fol$screen_name[i+86],
                        n = round(flt_n_2(active_fol$friends_count[i+86])),
                        retryonratelimit = TRUE)
  
  friend_3 <- rbind(friend_3,kk)
  
  if(i %% 5 == 0){
    Sys.sleep(5*60)
    message("sleep for 5 minutes")
    } 
}

```


```{r}
all_friend <- rbind(friend,friend_2,friend_3) %>%
  setNames(c("screen_name","user_id"))
all_friendzz <- left_join(all_friend, active_fol_x, by="screen_name")

algo_friend <- all_friendzz %>% select(user_id.x,user_id.y) %>%
  setNames(c("following","active_user"))

## filter algo_friend$active_user that are not availiable in algo_follower

missing_friend <- active_fol %>% filter(!user_id %in% algo_friend$active_user) %>%
  select(user_id,screen_name,friends_count) %>%
  filter(user_id %in% unique(algo_follower$active_user))





active_X <- data.frame(cbind(from = active_fol$user_id),
                       to = rep(algo$user_id,161))

algo_friend[algo_friend=="943736953274482688"] <- "TeamAlgoritma"

```

retrieve missing following
```{r}
miss_friend <- data.frame()

for (i in seq_along(missing_friend$screen_name)) {
  message("Getting followers for user #", i, "/16")
  kk <- get_friends(missing_friend$user_id[i],
                        n = round(flt_n_2(missing_friend$friends_count[i])),
                        retryonratelimit = TRUE)
  
  miss_friend <- rbind(miss_friend,kk)
  
  if(i %% 5 == 0){
    Sys.sleep(5*60)
    message("sleep for 5 minutes")
    } 
}


miss_friend_2_name <- algo_follower %>% filter(!algo_follower$active_user %in% miss_friend$user_id)
miss_friend_2_n <- active_fol %>% filter(user_id == miss_friend_2_name$active_user[1]) %>%
  select(user_id,screen_name,friends_count)

miss_friend_2 <- get_friends(miss_friend_2_name$active_user[1],
                             n = round(flt_n_2(miss_friend_2_n$friends_count)),
                             retryonratelimit = T)

miss_friend_all <- rbind(miss_friend,miss_friend_2)


```

```{r}
miss_friend_all <- miss_friend_all[,c(2,1)]
miss_friend_all <- miss_friend_all %>% setNames(c("following","active_user"))
algo_friend <- rbind(algo_friend,miss_friend_all)

algo_follower <- algo_follower[algo_follower$active_user!="1152196355881705473",]

f_algo <- algo_friend %>% filter(following == "943736953274482688")
not_f_algo <- algo_friend %>% filter(!algo_friend$active_user %in% f_algo$active_user)
not_f_df <- cbind(following = rep("943736953274482688",16),
                  active_user = unique(not_f_algo$active_user)) %>% data.frame()

algo_friend <- rbind(algo_friend,not_f_df)

algo_friend <- algo_friend[duplicated(algo_friend[1:2]),]
```

```{r}
un_active <- unique(algo_friend$active_user) %>% data.frame(stringsAsFactors = F) %>%
  setNames("user")

algo_mutual <- data.frame()

for (i in seq_along(un_active$user)){
  aa <- algo_friend %>% filter(active_user == un_active$user[i])
  bb <- aa %>% filter(aa$following %in% algo_follower$follower) %>%
    setNames(c("mutual","active_user"))
  
  algo_mutual <- rbind(algo_mutual,bb)
}

```
# Build Network

## Nodes
```{r}
nodes <- data.frame(V = unique(c(algo_mutual$mutual,algo_mutual$active_user)),
                    stringsAsFactors = F)

```

## Edges
```{r}
edges <- algo_mutual %>% setNames(c("from","to"))


```

## Graph
```{r}
network_ego1 <- graph_from_data_frame(d = edges, vertices = nodes, directed = F) %>%
  as_tbl_graph()

network_ego1 <- network_ego1 %>% 
  mutate(community = as.factor(group_walktrap())) %>%
  mutate(strength = centrality_degree()) %>%
  mutate(betweenness_c = centrality_betweenness(directed = F,normalized = T)) %>%
  mutate(closeness_c = centrality_closeness(normalized = T)) %>%
  mutate(degree_c = centrality_degree(normalized = T)) %>%
  mutate(page_rank = centrality_pagerank(directed = F)) %>%
  mutate(eigen = centrality_eigen(directed = F,scale = T))



cw <- cluster_walktrap(network_ego1)
member <- data.frame(v = 1:vcount(network_ego1), member = as.numeric(membership(cw)))
between_c <- betweenness(network_ego1,v = V(network_ego1),directed = F,normalized = T) %>%
  data.frame(stringsAsFactors = F) %>% setNames("betweenness")
between_c <- tibble::rownames_to_column(between_c,"V")

plot(simplify(g),
     vertex.size= 0.01, edge.arrow.size=0.001,
     vertex.label.cex = 0.75,vertex.label.color = "black"  ,
     vertex.frame.color = adjustcolor("white", alpha.f = 0),
     vertex.color = adjustcolor("white", alpha.f = 0),
     edge.color=adjustcolor(1, alpha.f = 0.15),
     display.isolates=FALSE,
     vertex.label=ifelse(page_rank(g)$vector > 0.1 , "important nodes", NA))

res_network <- simplify(contract(network_ego1, membership(cw)))

V(res_network)$size <- log(strength(res_network))*2
V(res_network)$label <- ifelse(strength(res_network)>=3, V(res_network)$name,NA)

lay <- layout_with_kk(res_network)
par(mar=c(0,0,0,0)); plot(res_network,layout = lay,
                          vertex.size = 10,
                          vertex.label = NA,
                          vertex.color = membership(cw))

V(network_ego1)$label <- ifelse(betweenness(network_ego1,v = V(network_ego1),
                                            directed = F,normalized = T) >= 0.1,
                                V(network_ego1)$name, NA)

lay2 <- layout_with_fr(network_ego1)
par(mar=c(0,0,0,0)); plot(simplify(network_ego1),layout = lay2,
                          vertex.size = 10, vertex.label.cex = 0.5,
                          vertex.color = membership(cw),
                          edge.color = adjustcolor(1,alpha.f = 0.15))


rain <- rainbow(89)
E(network_ego1)$color <- apply(as.data.frame(get.edgelist(network_ego1)),1,
                               function(x)ifelse(
                                 V(network_ego1)$community[x[1]]== V(network_ego1)$community[x[2]],
                                 rain[V(network_ego1)$community[x[1]]], "#00000000"))

com_f <- as.data.frame(table(V(network_ego1)$community))
com_f %>% arrange(-Freq)
```

```{r}
library(extrafont)
loadfonts(device = "win")
# windowsFonts()
```


```{r}
network_ego1 %>%
  filter(community %in% 1:3) %>%
  mutate(node_size = ifelse(degree_c >= 20,log(degree_c),0)) %>%
  ggraph(layout = "nicely") +
  geom_edge_fan(alpha = 0.25) +
  geom_node_point(aes(color = as.factor(community),size = node_size)) + 
  theme_graph() + theme(legend.position = "none",text = element_text(family = "mono")) +
  labs(title = "TeamAlgoritma Mutual Communities",
       subtitle = "Top 3 Community")

```

```{r}
network_ego1 %>%
  filter(community %in% 1:3) %>%
  mutate(node_label = ifelse(betweenness_c >= 0.05,name,"")) %>%
  mutate(node_size = ifelse(betweenness_c >= 0.05,log(betweenness_c)+1,0)) %>%
  ggraph(layout = "fr") +
  geom_edge_fan(alpha = 0.25) +
  geom_node_point(aes(color = as.factor(community),size = node_size)) +
  geom_node_text(aes(label = node_label,size = node_size), 
                 repel = T,color = "black", fontface = "bold") + 
  theme_graph() + theme(legend.position = "none")

```

```{r}
windowsFonts()
names(wf[wf=="TT Courier New"])
```

```{r}
product_net <- read.csv("data_input/product_net.csv",fileEncoding="UTF-8-BOM")
rownames(product_net) <- product_net[,1]
product_net[,1] <- NULL


product_net <- as.matrix(product_net)
dum_net <- graph_from_adjacency_matrix(product_net,mode = "undirected",diag = F)

ggg <- graph.adjacency(product_net)

dummnet <- get.edgelist(ggg) %>% as.data.frame() %>% setNames(c("from","to"))
write.csv(dummnet,"product_dum_net.csv",row.names = F)


```

To do next:
- find account that not included in algo_friend v
- subset account that not following "943736953274482688" in algo_friend v
- filter account yang saling follow"an dari algo_friend dan algo_follower v
- build ego network


```{r}
get_trends("Jakarta")
```

## Twitter Activity Network 2nd attempt

```{r}
eid <- search_tweets("#BersiapMenujuNewNormal",n = 18000,include_rts = T,retryonratelimit = T)

eid_df <- data.frame(lapply(ind,as.character),stringsAsFactors = F)

```

```{r}
edge_eid <- eid_df %>% select(created_at,screen_name,is_retweet,mentions_screen_name) %>%
  mutate(mentions_screen_name = sapply(mentions_screen_name,mention_clean)) %>% na.omit()

edge_eid <- edge_eid %>% 
  mutate(type = ifelse(is_retweet == "TRUE","retweet","mention"))

edge_eid <- edge_eid %>% select(screen_name,mentions_screen_name,type) %>%
  separate_rows(mentions_screen_name,sep = ",") %>% 
  setNames(c("from","to","type")) %>% count(from,to,type)


nodes_eid <- data.frame(V = unique(c(edge_eid$from,edge_eid$to)),
                        stringsAsFactors = F)

network_eid <- graph_from_data_frame(d = edge_eid, vertices = nodes_eid, directed = T) %>%
  as_tbl_graph()

network_eid <- network_eid %>% 
  activate(nodes) %>%
  mutate(community = group_walktrap(),
         degree = centrality_degree()) %>%
  activate(edges) %>%
  filter(!edge_is_loop())

```

```{r}
network_eid %>% 
  activate(nodes) %>%
  mutate(node_label = ifelse(degree >= 25,name,"")) %>%
  ggraph(layout = "kk") +
  geom_edge_arc(alpha = 0.05,aes(col = as.factor(type))) +
  geom_node_text(aes(label = node_label), repel = T,
                 color = "black", fontface = "bold") +
  theme_graph() + theme(legend.position = "bottom")
  
```

















## Twitter Activity network

```{r}
ind <- search_tweets("#IndonesiaTerserah",n = 18000,include_rts = F,retryonratelimit = T)

indrt <- search_tweets("#IndonesiaTerserah",n = 18000,include_rts = T,retryonratelimit = T,)
indrt_2 <- search_tweets("#IndonesiaTerserah",n = 18000,
                       include_rts = T,retryonratelimit = T,max_id = "1262618117730996224")
indrt_3 <- search_tweets("#IndonesiaTerserah",n = 18000,
                       include_rts = T,retryonratelimit = T,max_id = "1262260453104893954")
indrt_4 <- search_tweets("#IndonesiaTerserah",n = 18000,
                       include_rts = T,retryonratelimit = T,max_id = "1261875641659437058")

rl <- rate_limit()

rl[,2] == rl[,3]
rl[170,]

head(ind_df)
ind_df <- data.frame(lapply(ind,as.character),stringsAsFactors = F)

ind_df %>% arrange(as.numeric(retweet_count))

sum(as.numeric(ind_df$retweet_count))

table(as.factor(ind_df$is_retweet))

dumrt <- rtweet::get_retweeters(status_id = "1262309040237002752",n = 100)

indrt_3 %>% arrange(as.numeric(status_id))
range(indrt_2$created_at)

ind_all <- rbind(indrt,indrt_2,indrt_3)
ind_all <- data.frame(lapply(ind_all,as.character),stringsAsFactors = F)

scd_trd <- get_trends("Indonesia")

head(ind_all)

ind_all %>% filter(is_retweet == "TRUE")
```

```{r}
ind_rt <- ind_all %>% filter(is_retweet == "TRUE") %>%
  select(c(user_id,status_id,created_at,screen_name,retweet_count,retweet_status_id,retweet_screen_name))

ind_rt %>% arrange(-as.numeric(retweet_count))
```

```{r}
edges_act <- ind_rt %>% select(screen_name,retweet_screen_name,retweet_count) %>% 
  setNames(c("from","to","n"))
edges_act <- edges_act %>% mutate(type = rep("retweet"))

nodes_act <- data.frame(V = unique(c(edges_act$from,edges_act$to)),
                        stringsAsFactors = F)

network_act1 <- graph_from_data_frame(d = edges_act, vertices = nodes_act, directed = F) %>%
  as_tbl_graph()
```


```{r}
ind_mt <- ind_all %>% filter(is_retweet == "FALSE") %>%
  select(c(user_id,status_id,created_at,screen_name,mentions_screen_name))
```

```{r}
mention_clean <- function(x){
  if(grepl(",",x) == TRUE){
    gsub('^.|[^[:alnum:][:blank:]_,?&/\\-]',"",x)
  } else{
    x
  }
}
```

```{r}
ind_mt$mentions_screen_name <- sapply(ind_mt$mentions_screen_name,mention_clean)

edges_mt <- ind_mt %>% select(screen_name,mentions_screen_name) %>%
  na.omit() %>% separate_rows(mentions_screen_name,sep = ",") %>%
  setNames(c("from","to"))
edges_mt <- edges_mt %>% count(from,to) %>% mutate(type = rep("mention"))

nodes_mt <- data.frame(V = unique(c(edges_mt$from,edges_mt$to)),
                        stringsAsFactors = F)

network_mt1 <- graph_from_data_frame(d = edges_mt, vertices = nodes_mt, directed = F) %>%
  as_tbl_graph()
```

```{r}
nodes_actx <- rbind(nodes_act,nodes_mt) %>% distinct()
edges_actx <- rbind(edges_act,edges_mt)

network_actx <- graph_from_data_frame(d = edges_actx, vertices = nodes_actx, directed = T) %>%
  as_tbl_graph()

```
```{r}
network_actx <- network_actx %>%
  activate(nodes) %>%
  mutate(community = as.factor(group_walktrap()),
         degree = centrality_degree())

network_actx %>% activate(nodes) %>% arrange(-degree)
```

```{r}
network_actx %>% 
  activate(edges) %>%
  filter(!edge_is_loop()) %>%
  activate(nodes) %>%
  filter(community %in% 1:5) %>%
  top_n(50,degree) %>%
  mutate(node_label = ifelse(degree >= 30,name,"")) %>%
  ggraph(layout = "kk") +
  geom_edge_fan(aes(col  = type), alpha = 0.25) +
  geom_node_point(aes(col = community),show.legend = F)+
  geom_node_text(aes(label = node_label),repel = T,
                 show.legend = F, fontface = "bold") +
  theme_graph() + theme(legend.position = "bottom")
```


```{r}
network_act1 <- network_act1 %>%
  activate(nodes) %>% 
  mutate(weight = centrality_degree()) %>%
  arrange(-weight) %>%
  activate(edges) %>%
  mutate(type = rep("retweet"))


network_act1 %>% activate(nodes) %>% arrange(-weight)

network_act1 %>%
  activate(nodes) %>%
  mutate(community = as.factor(group_walktrap())) %>%
  mutate(id = row_number()) %>% 
  filter(community %in% 1:3) %>%
  top_n(1000,weight) %>%
  mutate(nodes_size = ifelse(weight >= 300, log(weight),0)) %>%
  mutate(nodes_label = ifelse(weight >= 300, name,"")) %>%
  ggraph(layout = "linear",circular = T, sort.by = "id") +  
  geom_edge_fan(alpha = 0.25) +
  geom_node_point(aes(size = nodes_size)) +
  geom_node_text(aes(label = nodes_label, size = nodes_size,col = community), 
                 repel = T,show.legend = F,fontface = "bold",
                 segment.colour = "slateblue") +
  theme_graph() + theme(legend.position = "none")
  

network_act1 %>%
  activate(nodes) %>%
  mutate(community = as.factor(group_walktrap())) %>%
  top_n(50,weight) %>%
  mutate(nodes_size = ifelse(weight >= 200, log(weight),0)) %>%
  mutate(nodes_label = ifelse(weight >= 200, name,"")) %>%
  ggraph(layout = "fr") +
  geom_edge_fan() +
  geom_node_point(aes(size = nodes_size, col = community)) +
  geom_node_text(aes(label = nodes_label), repel = T, 
                 show.legend = F, fontface = "bold", segment.colour = "slateblue") +
  theme_graph() + theme(legend.position = "none")


```

```{r}

```


## rate_limit() important row:
170 - search_tweets()



```{r}
mention_clean <- function(x){
  if(grepl(",",x) == TRUE){
    gsub('^.|[^[:alnum:][:blank:]_,?&/\\-]',"",x)
  } else{
    x
  }
}
```

```{r}
filter_ind_df <- ind_df %>%
  select(user_id,status_id,created_at,screen_name,retweet_count,mentions_screen_name,status_url) %>%
  mutate(created_at = ymd_hms(created_at),
         retweet_count = as.numeric(retweet_count),
         mentions_screen_name = sapply(mentions_screen_name,mention_clean)) %>%
  filter(retweet_count >= 30, mday(created_at) %in% 17:19) %>% arrange(-retweet_count)
  
  
range(filter_ind_df$created_at)

filter_ind_df %>% group_by(mday(created_at)) %>% summarise(tt=n())

sum(filter_ind_df$retweet_count)


```


```{r}
retweeter_id <- vector(mode = 'list', length = length(filter_ind_df$status_id))
names(retweeter_id) <- filter_ind_df$screen_name

for (i in seq_along(filter_ind_df$status_id)){
  message("Getting RT for tweet #",i," /105")
  retweeter_id[[i]] <- get_retweeters(filter_ind_df$status_id[i],n = 3500)
  
  if(i %% 50 == 0){
    message("Sleep for 15 minutes")
    Sys.sleep(15*60)
  }
}

rttst <- get_retweeters(filter_ind_df$status_id[1],n = 100)
```


```{r}
rt_df1 <- bind_rows(retweeter_id, .id="screen_name")
table(rt_df1$screen_name)
filter_ind_df$screen_name[50]
```













